\fakebf{HIV virulence evolution in structured epidemic models}

### 2016-05-30 poster/hivlhs_eeid2016.Rnw
still tweaking

%\documentclass[final,hyperref={pdfpagelabels=false}]{beamer}
\documentclass{beamer}
\usepackage{ebgaramond}
%% reset default
\renewcommand{\rmdefault}{cmss}
\usepackage{grffile}
\mode<presentation>{\usetheme{mcmaster}}

@@

%%%\title{\huge On the Persistence of Invading Pathogens}
\title{\LARGE HIV virulence evolution in structured epidemic models}

\author{\href{http://www.math.mcmaster.ca/bolker/}{Ben Bolker and Sang Woo Park}}
\email{\href{mailto:bolker@mcmaster.ca}{\texttt{bolker@mcmaster.ca}}}
\institute[McMaster University]{McMaster University, Hamilton, Ontario, Canada %%\\\vspace{5mm}\texttt{earn@math.mcmaster.ca}
}
\date[June 2016]{June 2016}

@@

\begin{block}{Summary}
\noindent
\hspace{-1.6cm}
Pathogens can evolve rapidly in response to changing
conditions (e.g., epidemic stage or public health interventions). 
Models of \textbf{eco-evolutionary dynamics} often
neglect important epidemiological processes, such as the 
dynamics of sexual partnerships. We
compared \textbf{models with a range of complexity} 
of partnership dynamics and extra-partnership contact.
\end{block}

@@

Spectrum of model complexity: 
\begin{itemize}
\item \textbf{pair formation}: instantaneous or delayed?
\item \textbf{extra-pair contact} (epc): present or absent?
\item \textbf{implicit model}: no explicit partnerships,
  force of infection expression derived from $\Ro$ of pair-formation
  model (without epc)
\item \textbf{random-mixing model}: standard SIR model
\end{itemize}

@@

%\pichskip{15pt}% Horizontal gap between picture and text
%\parpic[l][t]{%
%  \begin{minipage}{0.6\textwidth}
    \includegraphics[width=0.55\textwidth]{images/LHScrop.png}
%  \end{minipage}
%}
%%  \end{center}
%\caption{}
%\end{wrapfigure}
\begin{itemize}
  \item Latin hypercube sampling: parameters from
    \cite{champredon_hiv_2013}
  \item parameters calibrated across models to the same \textbf{initial epidemic growth rate} ($r$)
\end{itemize}
\end{block}
}
\end{minipage}
\end{beamercolorbox}
\end{column}

@@

            \begin{block}{Univariate summary}
              \includegraphics[width=0.95\textwidth]{figure/univ.pdf}
            \end{block}
            \vspace{0.5cm}

>>>>

%\documentclass[final,hyperref={pdfpagelabels=false}]{beamer}
\documentclass{beamer}
\usepackage{ebgaramond}
\newcommand{\fakebf}{\fontfamily{mdugm}\fontseries{b}\selectfont}
%% reset default
\renewcommand{\rmdefault}{cmss}
\usepackage{grffile}
\mode<presentation>{\usetheme{mcmaster}}

@@

%%%\title{\huge On the Persistence of Invading Pathogens}
\title{\fakebf{HIV virulence evolution in structured epidemic models}}

\author{\href{http://www.math.mcmaster.ca/bolker/}{Ben Bolker and Sang Woo Park}}
\email{\href{mailto:bolker@mcmaster.ca}{\texttt{bolker@mcmaster.ca}}}
\institute[McMaster University]{McMaster University, Hamilton, Ontario, Canada 
%%\\\vspace{5mm}\texttt{earn@math.mcmaster.ca}
}
%\institute[]{}
\date[June 2016]{June 2016}

@@

\vspace{-2.4 cm} % shouldn't need this??
\begin{block}{Summary}
\noindent
\hspace{-1.6cm}
Pathogens can evolve rapidly in response to changing
conditions (e.g., epidemic stage or public health interventions). 
Models of \textbf{eco-evolutionary dynamics} often
neglect important epidemiological processes, such as the 
dynamics of sexual partnerships. We
compared \textbf{models with a range of complexity} 
of partnership dynamics and extra-partnership contact.
\end{block}

@@

\textbf{infection} from (1) inf. partner (discordant couples);
(2) other coupled inf.; (3) uncoupled inf.

\vspace{0.2cm}
Model choices:
\begin{itemize}
\item \textbf{pair formation}: instantaneous or delayed?
\item \textbf{extra-pair contact} (epc): present or absent?
\item \textbf{implicit model}: no explicit partnerships,
  force of infection expression derived from $\Ro$ of pair-formation
  model (without epc)
\item \textbf{random-mixing model}: standard SIR model
\end{itemize}

@@

%\pichskip{15pt}% Horizontal gap between picture and text
%\parpic[l][t]{%
%  \begin{minipage}{0.6\textwidth}
    \includegraphics[width=0.25\textwidth]{images/LHScrop.png}
%  \end{minipage}
%}
%%  \end{center}
%\caption{}
%\end{wrapfigure}
\begin{itemize}
  \item Latin hypercube sampling: parameters from
    \cite{champredon_hiv_2013}
  \item parameters calibrated across models to the same \textbf{initial epidemic growth rate} ($r$)
\end{itemize}
\end{block}
}
\end{minipage}
\end{beamercolorbox}
\end{column}

@@

            \begin{block}{Univariate summaries}
              \includegraphics[width=0.7\textwidth]{figure/univ_scheme.pdf}

              \vspace{1cm}
              \includegraphics[width=0.95\textwidth]{figure/univ.pdf}
            \end{block}
            \vspace{0.5cm}
